Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming

### 2023-01-10 slides.Rmd
Tue Jan 10 19:00:08 CET 2023: update-remote.sh

# Create a sample data frame
df <- read.csv("/Users/rmn/github/master_thesis/data/summary_table_final_fit.csv", sep=",")
print(df)

@@

# Apply the function to the data frame
df$DAE.GP <- mapply(bold_min, df$DAE_GP, df$Pre_Trained_DAE_GP)
)

>>>>

# Create a sample data frame
df <- read.csv("/Users/rmn/github/master_thesis/data/summary_table_final_fit.csv", sep=",")

@@

# Apply the function to the data frame
df <- mapply(bold_min, df$DAE_GP, df$Pre_Trained_DAE_GP)
#print(df)
